### 2018-07-22 experiments.tex
ok

>>>>

\subsubsection{Mutation analysis}

We ran 2,350 mutants of pyfakefs.  Using the failure determinism check
in 60 second test runs let us kill 98 mutants that were not killed
during 60 seconds of testing without a reference or the failure
determinism check, using the exact same random seed (and thus same
sequence of test operations, only changing the specification).  Of
these additional mutants, 71 could not even be killed by 120
seconds of testing using differential testing with the Mac OS X file system
as a reference.  That is, more than 2/3 of the mutants killed by the
failure determinism check could not be killed even with a much
stronger specification that lacked a check for failure determinism,
and was given more time to execute.  To put this in perspective, the
mutation kill rate for the test harness with 60 seconds and no
differential comparison was 37.1\%; for the full differential harness
with 120 seconds it was 60\%.

There is a price to be paid:  for mutants that could be killed both
with and without the failure determinism check, the mean time to kill
the mutant was 0.006 seconds larger when the failure determinism
check was included, and this change was significant by Wilcoxon test
at $p < 1 \times 10^{-15}$.

In order to further investigate the additional specification power
provided by failure determinism checks, we inspected the mutants
killed by the failure determinism check but not by full differential
testing.  The largest category of mutants not killed (22 of the 71 mutants) was what we refer
to as ``exception swallowing'' mutants, which transform a Python
statement into the same statement, but wrapped in a {\tt try} block
with a catch that ignores any raised exceptions.  It is easy to
understand that such mutants introduce faults in the handling of
errors, and thus would tend to cause failurel nondeterminism.
